---
title: "fars_functions examples"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
#load fars package
```{r setup}
library(fars)
```
#make_filename function makes a file name with a given year of interest
```{r make_filename} 
print(make_filename(2013))
```
#fars_read function reads in data file with a given filename
```{r fars_read} 
dat<-fars_read(make_filename(2013))
head(dat)
```
#fars_read_years function reads in data of a given year and returns the months and year variables
```{r fars_read_years}
dat<-fars_read_years(2013)
head(dat)
```
#fars_summarize_years function makes a table of total number of observations by year and month
```{r fars_summarize_years}
fars_summarize_years(2013)
```
#fars_map_state function creates a map of a given state
#at a given year
```{r fars_map_state}
fars_map_state(state.num=10,year=2013)
```
